---
title: "Biomarkers and genetics DataSchema"
output: html_document
---

# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opal)
library(data.table)
# Create an opal object with the login information
erasmus_opal <-opal.login('agurer','1234tamamw','https://obiba.erasmusmc.nl')
#Login to Opal server and assign the content of the LASA table(s) to your RStudio environment

# LASA2B
opal.assign.table.tibble(erasmus_opal, 'LASA2B', 'LASA.LASA2B_biodata',variables = list('bmalbumi','bmtsh','bmcrp','bmtrigly','bmfreet4','bmvitd25', "bmvitd25st"))
LASA2B <- opal.execute(erasmus_opal,'LASA2B')

# LASA2G
opal.assign.table.tibble(erasmus_opal, 'LASA2G', 'LASA.LASA2G_biodata',variables = list('gmalbumi',"gmvitd25", "gmvitd25st"))
LASA2G <- opal.execute(erasmus_opal,'LASA2G')

```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
bio_LASA2_0 <- data.frame(id = LASA2B$id)
bio_LASA2_2 <- data.frame(id = LASA2G$id)


```
## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
#opal.logout(erasmus_opal) 
```
###After the other steps of harmonization is done, replacing all -1's and -2's with NA's and checking the datasets

```{r, echo=FALSE}
bio_LASA2_0[bio_LASA2_0==-1|bio_LASA2_0==-2]<-NA
str(bio_LASA2_0)
View(bio_LASA2_0)

bio_LASA2_2[bio_LASA2_2==-1|bio_LASA2_2==-2]<-NA
str(bio_LASA2_2)

```
# Table of Contents
1. [Non-genetic Biomarker subdomain](#Non-genetic-biomarker-subdomain)
2. [Genetic Biomarker subdomain](#Genetic-biomarker-subdomain)

# Non-genetic Biomarkers subdomain

### **Variable label**: C-Reactive Protbein  
**Variable name**: BIO_CRP_0    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  complete
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, MESA, RS, HAPIEE (baseline only)  
**Harmonization comment**:There are 2 variables for CRP in LASA1: bmcrp and bmhscrp. And possibly bmhscrp is preferred as the LASA documentation states: 
"Please note that CRP levels have also been determined directly after blood sampling (both in 1992/93 and in 1995/96), but this has been done for respondents in the Zwolle region only (N=384; see “Docu bloedbepaling B en C). However, for complete use of all available CRP data, it is strongly recommended to use data from file B+C861 (inflammatory markers), because this file includes the measurements of respondents in all regions. Also, the CRP determination in Zwolle was performed with a less sensitive assay than the CRP determination in the blood samples from all regions." C861 includes bmhscrp, not bmcrp. But for LASA2 we only have bmcrp measure. If we use this one it might not be comparable with LASA1 if we do not use the bmcrp for LASA1 as well. However, in that case the number of NAs will be very high and that might not be an equally reliable measure.  

**R script**:  
```{r, echo=TRUE}
#Checking the varibale bmcrp (Blood: CRP mG/L)

table(LASA2B$bmcrp, useNA = "always")
sum(LASA2B$bmcrp!=-2)

bio_LASA2_0$bio_crp_0<-LASA2B$bmcrp
table(bio_LASA2_0$bio_crp_0, useNA = "always")
summary(bio_LASA2_0$bio_crp_0)
is.numeric(bio_LASA2_0$bio_crp_0)
```
### **Variable label**: C-Reactive Protein  
**Variable name**: BIO_CRP_1    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}


```

### **Variable label**: C-Reactive Protein  
**Variable name**: BIO_CRP_2    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:    

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: C-Reactive Protein  
**Variable name**: BIO_CRP_3    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L   
**Category coding**:   

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: C-Reactive Protein  
**Variable name**: BIO_CRP_4    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:   

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: C-Reactive Protein  
**Variable name**: BIO_CRP_5    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: C-Reactive Protein  
**Variable name**: BIO_CRP_6    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:   

**Harmonization status**:  impossibe
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: BIO_TSH_0    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**:

**Harmonization status**: complete 
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
table(LASA2B$bmtsh, useNA = "always")
bio_LASA2_0$bio_tsh_0<-LASA2B$bmtsh
table(bio_LASA2_0$bio_tsh_0, useNA = "always")
summary(bio_LASA2_0$bio_tsh_0)

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: BIO_TSH_1    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS

**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: BIO_TSH_2    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: BIO_TSH_3    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: BIO_TSH_4    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: BIO_TSH_5    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: BIO_TSH_6    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Thyroxine  
**Variable name**: BIO_T4_0    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**:

**Harmonization status**:  complete  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
table(LASA2B$bmfreet4 , useNA = "always")
bio_LASA2_0$bio_t4_0<-LASA2B$bmfreet4
table(bio_LASA2_0$bio_t4_0, useNA = "always")
summary(bio_LASA2_0$bio_t4_0)

```
### **Variable label**: Thyroxine  
**Variable name**: BIO_T4_1    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**Harmonization comment**: There are 2 different variables for T4: cmft4 (free T4 (pmol/l)) and cmfreet4 (Blood: free T4 pMOL/L)

**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Thyroxine  
**Variable name**: BIO_T4_2    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Thyroxine  
**Variable name**: BIO_T4_3    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Thyroxine  
**Variable name**: BIO_T4_4    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Thyroxine  
**Variable name**: BIO_T4_5    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Thyroxine  
**Variable name**: BIO_T4_6    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Albumin  
**Variable name**: BIO_ALB_0    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  complete  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
table(LASA2B$bmalbumi , useNA = "always")
bio_LASA2_0$bio_alb_0<-LASA2B$bmalbumi
table(bio_LASA2_0$bio_alb_0, useNA = "always")
summary(bio_LASA2_0$bio_alb_0)

```
### **Variable label**: Albumin  
**Variable name**: BIO_ALB_1    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: BIO_ALB_2    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  complete  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
table(LASA2G$gmalbumi , useNA = "always")
bio_lasa2_2$bio_alb_2<-LASA2G$gmalbumi
table(bio_lasa2_2$bio_alb_2, useNA = "always")
summary(bio_lasa2_2$bio_alb_2)

```
### **Variable label**: Albumin  
**Variable name**: BIO_ALB_3    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Albumin  
**Variable name**: BIO_ALB_4    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: N/A (continuous variable)  


**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Albumin  
**Variable name**: BIO_ALB_5    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Albumin  
**Variable name**: BIO_ALB_6    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: BIO_ALT_0    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**Harmonization comment**: Previous comment says it is available in LASA but it is not in LASA1 or LASA2  

**R script**:  
```{r, echo=TRUE}
```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: BIO_ALT_1    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: BIO_ALT_2    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: BIO_ALT_3    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: BIO_ALT_4    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: BIO_ALT_5    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
 
```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: BIO_ALT_6    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
 
```
### **Variable label**: Vitamin D 
**Variable name**: BIO_VitD_0    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 
**Harmonization status**:  complete
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**Harmonization comment**:There are 2 variables: cmvitd25st (serum: 25-hydroxyvitamin D (25(OH)D), nmol/L, ODIN-standardized) and 
cmvitd25 (serum: 25-hydroxyvitamin D (25(OH)D), nmol/L). "In 2015, serum 25(OHD) values were standardized using the Vitamin D Standardization Program (VDSP) protocol as part of the European ODIN study" From NIH website (https://ods.od.nih.gov/Research/vdsp.aspx): "art of the ODS Vitamin D Initiative, VDSP is an international collaborative effort to standardize the laboratory measurement of vitamin D status." So should we use the standardized measure to make it more comparable across time and studies. However, if other cohorts didn't use this measure maybe there is not much point?

**R script**:  
```{r, echo=TRUE}

table(LASA2B$bmvitd25st, useNA = "always")
table(LASA2B$bmvitd25, useNA = "always")

summary(LASA2B$bmvitd25)
summary(LASA2B$bmvitd25st)

bio_LASA2_0$bio_vitd_0<-LASA2B$bmvitd25st
#1 ng/ml =0.400641 nmol/l
bio_LASA2_0$bio_vitd_0[bio_LASA2_0$bio_vitd_0==-1]<-NA
bio_LASA2_0$bio_vitd_0<-bio_LASA2_0$bio_vitd_0*0.400641
table(bio_LASA2_0$bio_vitd_0, useNA = "always")
summary(bio_LASA2_0$bio_vitd_0)

```
### **Variable label**: Vitamin D 
**Variable name**: BIO_VitD_1    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**: impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  

**R script**:  
```{r, echo=TRUE}
```
### **Variable label**: Vitamin D 
**Variable name**: BIO_VitD_2    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  complete  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}
table(LASA2G$gmvitd25st, useNA = "always")
table(LASA2G$gmvitd25, useNA = "always")

summary(LASA2G$gmvitd25)
summary(LASA2G$gmvitd25st)

bio_lasa2_2$bio_vitd_2<-LASA2G$gmvitd25st
#1 ng/ml =0.400641 nmol/l
bio_lasa2_2$bio_vitd_2[bio_lasa2_2$bio_vitd_2==-1]<-NA
bio_lasa2_2$bio_vitd_2<-bio_lasa2_2$bio_vitd_2*0.400641
table(bio_lasa2_2$bio_vitd_2, useNA = "always")
summary(bio_lasa2_2$bio_vitd_2)

```
### **Variable label**: Vitamin D 
**Variable name**: BIO_VitD_3    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Vitamin D 
**Variable name**: BIO_VitD_4    
**Variable description**: Vitamin D measured in serum (fresh and frozen).      
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Vitamin D 
**Variable name**: BIO_VitD_5    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Vitamin D 
**Variable name**: BIO_VitD_6    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 
**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}



```
### **Variable label**: Triglycerides 
**Variable name**: BIO_TG_0    
**Variable description**: Triglycerides measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  complete  
**Harmonization comment**: Available in 7 studies: CLSA, HUNT, LASA, RECORD, MESA, RS, HAPIEE (baseline only) 
**R script**:  
```{r, echo=TRUE}
table(LASA2B$bmtrigly, useNA = "always")
bio_LASA2_0$bio_tg_0<-LASA2B$bmtrigly
table(bio_LASA2_0$bio_tg_0, useNA = "always")
summary(bio_LASA2_0$bio_tg_0)

```
### **Variable label**: Triglycerides 
**Variable name**: BIO_TG_1    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  impossible   
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 

**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: BIO_TG_2    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  

**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Triglycerides 
**Variable name**: BIO_TG_3    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Triglycerides 
**Variable name**: BIO_TG_4    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  impossible  
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Triglycerides 
**Variable name**: BIO_TG_5    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  impossible  
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Triglycerides 
**Variable name**: BIO_TG_6    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```

# Genetic Biomarker subdomain

### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_0   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_1   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_2   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A 
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_3   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_4   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_5   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_6   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_0   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_1   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_2   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_3   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_4   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_5   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_6   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_0   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_1   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_2   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_3   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_4   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_5   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_6   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_0   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_1   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_2   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_3   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_4   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_5   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_6   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_0   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_1   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_2   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_3   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_4   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_5   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_6   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
