---
title: "Biomarkers and genetics DataSchema"
output: html_document
---

# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opalr)
library(data.table)
# Create an opal object with the login information
erasmus_opal <-opal.login()
#Login to Opal server and assign the content of the LASA table(s) to your RStudio environment

# LASA1B
opal.assign.table.tibble(erasmus_opal, 'LASA1B', 'LASA.LASA1B_biodata',variables = list('bmalbumi','bmtsh','bmcrp','bmtrigly','bmfreet4','bmhscrp'))
LASA1B <- opal.execute(erasmus_opal,'LASA1B')

# LASA1C
opal.assign.table.tibble(erasmus_opal, 'LASA1C', 'LASA.LASA1C_biodata',variables = list('cmalbumi','cmtsh','cmcrp','cmtrigly','cmfreet4','cmhscrp', "cmvitd25", "cmvitd25st","cmtsh2", "cmtrigl2", "cmft4", "cmft3"))
LASA1C <- opal.execute(erasmus_opal,'LASA1C')


# LASA1G
opal.assign.table.tibble(erasmus_opal, 'LASA1G', 'LASA.LASA1G_biodata',variables = list('gmalbumi',"gmvitd25", "gmvitd25st"))
LASA1G <- opal.execute(erasmus_opal,'LASA1G')

```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
bio_LASA1_0 <- data.frame(id = LASA1B$id)
bio_LASA1_1 <- data.frame(id = LASA1C$id)
bio_LASA1_6 <- data.frame(id = LASA1G$id)


```
## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
#opal.logout(erasmus_opal) 
```
# Table of Contents
1. [Non-genetic Biomarker subdomain](#Non-genetic-biomarker-subdomain)
2. [Genetic Biomarker subdomain](#Genetic-biomarker-subdomain)

# Non-genetic Biomarkers subdomain

### **Variable label**: C-Reactive Protbein  
**Variable name**: bio_crp_0    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  complete
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, MESA, RS, HAPIEE (baseline only).  Values from frozen and fresh are closely correlated so both variables were used for harmoniztation. Values from frozen were taken first, and if there were missing values, values were taken from fresh.    
**R script**:  
```{r, echo=TRUE}
bio_LASA1_0$bio_crp_0 <- ifelse(
                          is.na(LASA1B$bmhscrp), 
                                LASA1B$bmcrp, 
                                LASA1B$bmhscrp)
bio_LASA1_0[bio_LASA1_0$bio_crp_0 == -1 | 
            bio_LASA1_0$bio_crp_0 == -2,]$bio_crp_0 <- NA
```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_1    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  complete
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS. Values from frozen and fresh are closely correlated so both variables were used for harmoniztation. Values from frozen were taken first, and if there were missing values, values were taken from fresh.     
**R script**:  
```{r, echo=TRUE}
bio_LASA1_1$bio_crp_1 <- ifelse(
                          is.na(LASA1C$cmhscrp), 
                                LASA1C$cmcrp,
                                LASA1C$cmhscrp)
bio_LASA1_1[bio_LASA1_1$bio_crp_1 == -1 | 
            bio_LASA1_1$bio_crp_1 == -2,]$bio_crp_1<-NA
```

### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_2    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:    

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_3    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L   
**Category coding**:   

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_4    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:   

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_5    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_6    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:   

**Harmonization status**:  impossibe
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_0    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**:

**Harmonization status**: complete     
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS. Only values from fresh were available in this wave.  

**R script**:  
```{r, echo=TRUE}

#**Question for cohort**: LASA documentation states the information on thyroid hormone is collected only at time point C, but we have it at time B. In time point C, the measurement they refer to for thyroid function is cmtsh2, not cmtsh. bmths, cmths measures are referred under "Routine measurements: Albumin and cholesterol". What is the difference?
  
bio_LASA1_0$bio_tsh_0 <- LASA1B$bmtsh
bio_LASA1_0[bio_LASA1_0$bio_tsh_0 == -1 |
            bio_LASA1_0$bio_tsh_0 == -2,]$bio_tsh_0 <- NA

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_1    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  complete
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS. Values from frozen and fresh are closely correlated so both variables were used for harmoniztation. Values from frozen were taken first, and if there were missing values, values were taken from fresh.    


**R script**:  
```{r, echo=TRUE}

#**Question for cohort**: There are two variables: cmtsh: Blood: TSH mU/L abd cmtsh2: thyroid-stimulating hormone (mU/l). There are a lot more missing values in cmtsh, and the documentation refers to cmtsh2 for TSH hormone; however we probably should ask about the difference. cmtsh is under Routine measurements: Albumin and cholesterol category. Which one should we refer to?

bio_LASA1_1$bio_tsh_1 <- ifelse(
                          is.na(LASA1C$cmtsh2),
                                LASA1C$cmtsh,
                                LASA1C$cmtsh2)
bio_LASA1_1[bio_LASA1_1$bio_tsh_1 == -1 | 
            bio_LASA1_1$bio_tsh_1 == -2,]$bio_tsh_1 <- NA
```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_2    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_3    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_4    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_5    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_6    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_0    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**:

**Harmonization status**:  complete      
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS. Only values from fresh are available at this wave. Only values from fresh were available for this wave.  
**R script**:  
```{r, echo=TRUE}
#**Question for cohort**: LASA documentation states the information on thyroid hormone is collected only at time point C, but we have it at time B. What is bmfreet4, the variable at time B?

bio_LASA1_0$bio_t4_0 <- LASA1B$bmfreet4
bio_LASA1_0[bio_LASA1_0$bio_t4_0 == -1 |
            bio_LASA1_0$bio_t4_0 == -2,]$bio_t4_0 <- NA
```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_1    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**:

**Harmonization status**:  complete  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS. Values from frozen and fresh are closely correlated so both variables were used for harmoniztation. Values from frozen were taken first, and if there were missing values, values were taken from fresh.    

**R script**:  
```{r, echo=TRUE}
bio_LASA1_1$bio_t4_1 <- ifelse(
                         is.na(LASA1C$cmfreet4),
                               LASA1C$cmft4,
                               LASA1C$cmfreet4)
bio_LASA1_1[bio_LASA1_1$bio_t4_1 == -1 | 
            bio_LASA1_1$bio_t4_1==-2,]$bio_t4_1 <- NA
```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_2    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_3    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_4    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_5    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_6    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_0    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  complete  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS. Only values from frozen were available in this wave.   
**R script**:  
```{r, echo=TRUE}
bio_LASA1_0$bio_alb_0<-LASA1B$bmalbumi
bio_LASA1_0[bio_LASA1_0$bio_alb_0 == -1 | 
            bio_LASA1_0$bio_alb_0 == -2,]$bio_alb_0 <- NA
```
### **Variable label**: Albumin  
**Variable name**: bio_alb_1    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  complete 
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS. Only values from frozen were available in this wave.   
**R script**:  
```{r, echo=TRUE}
bio_LASA1_1$bio_alb_1<-LASA1C$cmalbumi
bio_LASA1_1[bio_LASA1_1$bio_alb_1 == -1 | 
            bio_LASA1_1$bio_alb_1 == -2,]$bio_alb_1 <- NA
```
### **Variable label**: Albumin  
**Variable name**: bio_alb_2    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_3    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_4    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: N/A (continuous variable)  


**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_5    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_6    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
bio_LASA1_6$bio_alb_6<-LASA1G$gmalbumi
bio_LASA1_6[bio_LASA1_6$bio_alb_6 == -1 | 
            bio_LASA1_6$bio_alb_6 == -2,]$bio_alb_6 <- NA
```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_0    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_1    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_2    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_3    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_4    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_5    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_6    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_0    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 
**Harmonization status**:  impossible
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_1    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**: complete   
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS. There are 2 variables of vitmain D available, the Odin standadised values were used for harmonization.  


**R script**:  
```{r, echo=TRUE}
# conversion: 0.400641
bio_LASA1_1$bio_vitd_1 <- LASA1C$cmvitd25st
bio_LASA1_1[bio_LASA1_1$bio_vitd_1 == -1 | 
            bio_LASA1_1$bio_vitd_1 == -2,]$bio_vitd_1 <- NA
bio_LASA1_1$bio_vitd_1 <- bio_LASA1_1$bio_vitd_1*0.400641
```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_2    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_3    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_4    
**Variable description**: Vitamin D measured in serum (fresh and frozen).      
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_5    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  complete    
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS. There are 2 variables of vitmain D available, the Odin standadised values were used for harmonization.    
**R script**:  
```{r, echo=TRUE}
bio_LASA1_6$bio_vitd_6 <- LASA1G$gmvitd25st
bio_LASA1_6[bio_LASA1_6$bio_vitd_6 == -1 | 
            bio_LASA1_6$bio_vitd_6 == -2,]$bio_vitd_6 <-NA
bio_LASA1_6$bio_vitd_6 <- bio_LASA1_6$bio_vitd_6*0.400641
```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_6    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 
**Harmonization status**:  impossible    
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_0    
**Variable description**: Triglycerides measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  complete  
**Harmonization comment**: Available in 7 studies: CLSA, HUNT, LASA, RECORD, MESA, RS, HAPIEE (baseline only). Values are from non-fasting participants.   
**R script**:  
```{r, echo=TRUE}
bio_LASA1_0$bio_tg_0<-LASA1B$bmtrigly
bio_LASA1_0[bio_LASA1_0$bio_tg_0 == -1 | 
            bio_LASA1_0$bio_tg_0 == -2,]$bio_tg_0 <- NA
```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_1    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  complete  
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 


**R script**:  
```{r, echo=TRUE}
#**Question for cohort**: There are 2 variables in the dataset.  cmtrigly (Blood: triglycerids mMOL/L), cmtrigl2 (Blood: triglycerids mmol/L). cmtrigl2 is specifically under Cholesterol, triglycerides and fructosamin, cmtrigly is under routine measures. For bmtrigly, for collection point B, the documentation mentions -2's are from the Oss region, maybe these routine measure were not taken from that region at time point C as well?

# # propostion 1
# bio_LASA1_1$bio_tg_1 <- LASA1C$cmtrigl2
# bio_LASA1_1[bio_LASA1_1$bio_tg_1 == -1 | 
#             bio_LASA1_1$bio_tg_1 == -2,]$bio_tg_1 <- NA
# # propostion 2
# bio_LASA1_1$bio_tg_1 <- ifelse(
#                          is.na(LASA1C$cmtrigl2),
#                                LASA1C$cmtrigly,
#                                LASA1C$cmtrigl2)
# bio_LASA1_1[bio_LASA1_1$bio_tg_1 == -1 | 
#             bio_LASA1_1$bio_tg_1 == -2,]$bio_tg_1 <- NA
```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_2    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  

**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_3    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_4    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  impossible  
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_5    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  impossible  
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_6    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```

# Genetic Biomarker subdomain

### **Variable label**: RS7412 
**Variable name**: bio_rs7412_0   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_1   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_2   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A 
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_3   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_4   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_5   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_6   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_0   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_1   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_2   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_3   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_4   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_5   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_6   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_0   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_1   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_2   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_3   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_4   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_5   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_6   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_0   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_1   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_2   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_3   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_4   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_5   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Rs6265
**Variable name**: bio_rs6265_6   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_0   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_1   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_2   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_3   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_4   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_5   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_6   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
