---
title: "Biomarkers and genetics DataSchema"
output: html_document
---

# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opalr)
library(data.table)
# Create an opal object with the login information
erasmus_opal <-opal.login()
#Login to Opal server and assign the content of the LASA table(s) to your RStudio environment
# HUNT1
# opal.assign.table.tibble(erasmus_opal, 'HUNT1', 'HUNT.HUNT1',variables = list(''))
# HUNT1 <- opal.execute(erasmus_opal,'HUNT1')


opal.assign.table.tibble(erasmus_opal, 'HUNT1GWAS', 'HUNT.HUNT1GWAS' )
HUNT1_G <- opal.execute(erasmus_opal,'HUNT1GWAS')



# HUNT2
opal.assign.table.tibble(erasmus_opal, 'HUNT2', 'HUNT.HUNT2',variables = list('SeTrig_NT2BLM'))
HUNT2 <- opal.execute(erasmus_opal,'HUNT2')

opal.assign.table.tibble(erasmus_opal, 'HUNT2GWAS', 'HUNT.HUNT2GWAS' )
HUNT2_G <- opal.execute(erasmus_opal,'HUNT2GWAS')


# HUNT3
opal.assign.table.tibble(erasmus_opal, 'HUNT3', 'HUNT.HUNT3',variables = list('SemicroCRP_NT3BLM','SeTSH','SeT4_NT3BLM','SeTrig','SeTSH_NT3BLM', 'SeALAT_NT3BLM', 'SeTrig_NT3BLM'))
HUNT3 <- opal.execute(erasmus_opal,'HUNT3')

opal.assign.table.tibble(erasmus_opal, 'HUNT3GWAS', 'HUNT.HUNT3GWAS' )
HUNT3_G <- opal.execute(erasmus_opal,'HUNT3GWAS')

```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}

#HUNT1<-merge(HUNT1, HUNT1_G, by="id", all=TRUE)
HUNT2<-merge(HUNT2, HUNT2_G, by="id", all=TRUE)
HUNT3<-merge(HUNT3, HUNT3_G, by="id", all=TRUE)

bio_HUNT_0 <- data.frame(id = HUNT1_G$id)
bio_HUNT_1 <- data.frame(id = HUNT2$id)
bio_HUNT_2 <- data.frame(id = HUNT3$id)
```
## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
#opal.logout(erasmus_opal) 
```
# Table of Contents
1. [Non-genetic Biomarker subdomain](#Non-genetic-biomarker-subdomain)
2. [Genetic Biomarker subdomain](#Genetic-biomarker-subdomain)

# Non-genetic Biomarkers subdomain

### **Variable label**: C-Reactive Protbein  
**Variable name**: bio_crp_0    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_1    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```

### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_2    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_3    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L   
**Category coding**:   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_4    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_5    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_6    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:   

**Harmonization status**:  impossibe
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_0    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**:

**Harmonization status**: impossible       
**Harmonization comment**:    

**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_1    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:    


**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_2    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  complete    
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
bio_HUNT_2$bio_tsh_2 <- HUNT3$SeTSH_NT3BLM
```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_3    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_4    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_5    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_6    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_0    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**:

**Harmonization status**:  impossible        
**Harmonization comment**:    
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_1    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**:

**Harmonization status**:  impossible    
**Harmonization comment**:      

**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_2    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  complete    
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
bio_HUNT_2$bio_t4_2 <- HUNT3$SeT4_NT3BLM
```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_3    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_4    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_5    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_6    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_0    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible    
**Harmonization comment**:      
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_1    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible   
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_2    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_3    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_4    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: N/A   


**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_5    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_6    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible      
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_0    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_1    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_2    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
bio_HUNT_2$bio_alt_2 <- HUNT3$SeALAT_NT3BLM
```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_3    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_4    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_5    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_6    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_0    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 
**Harmonization status**:  impossible
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_1    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**: impossible     
**Harmonization comment**:  

**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_2    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_3    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_4    
**Variable description**: Vitamin D measured in serum (fresh and frozen).      
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_5    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  impossible      
**Harmonization comment**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_6    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 
**Harmonization status**:  impossible    
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_0    
**Variable description**: Triglycerides measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible    
**Harmonization comment**:   
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_1    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  complete  
**Harmonization comment**:  


**R script**:  
```{r, echo=TRUE}
bio_HUNT_1$bio_tg_1 <- HUNT2$SeTrig_NT2BLM
```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_2    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  complete    

**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
bio_HUNT_2$bio_tg_2 <- HUNT3$SeTrig_NT3BLM
```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_3    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_4    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_5    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_6    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```

# Genetic Biomarker subdomain

### **Variable label**: RS7412 
**Variable name**: bio_rs7412_0   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**: complete     
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_1   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**: complete     
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_2   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A 
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**: complete     
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_3   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_4   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_5   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_6   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_0   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**: complete     
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_1   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  complete    
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_2   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  complete    
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_3   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_4   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_5   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_6   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_0   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**: complete     
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_1   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  complete    
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_2   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:   complete   
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_3   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_4   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_5   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_6   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_0   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  complete    
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_1   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**: complete     
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_2   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  complete    
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_3   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_4   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_5   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```

### **Variable label**: Rs6265
**Variable name**: bio_rs6265_6   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_0   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**: complete   
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_1   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  complete    
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_2   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**: complete     
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_3   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_4   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_5   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_6   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
