---
title: "Biomarkers and genetics DataSchema"
output: html_document
---

# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opalr)
library(data.table)
# Create an opal object with the login information
erasmus_opal <-opal.login()
#Login to Opal server and assign the content of the LASA table(s) to your RStudio environment

# LASA2B
opal.assign.table.tibble(erasmus_opal, 'LASA2B', 'LASA.LASA2B_biodata',variables = list('bmalbumi','bmtsh','bmcrp','bmtrigly','bmfreet4','bmvitd25', "bmvitd25st"))
LASA2B <- opal.execute(erasmus_opal,'LASA2B')

# LASA2G
opal.assign.table.tibble(erasmus_opal, 'LASA2G', 'LASA.LASA2G_biodata',variables = list('gmalbumi',"gmvitd25", "gmvitd25st"))
LASA2G <- opal.execute(erasmus_opal,'LASA2G')

```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
bio_LASA2_0 <- data.frame(id = LASA2B$id)
bio_LASA2_2 <- data.frame(id = LASA2G$id)


```
## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
#opal.logout(erasmus_opal) 
```

# Table of Contents
1. [Non-genetic Biomarker subdomain](#Non-genetic-biomarker-subdomain)
2. [Genetic Biomarker subdomain](#Genetic-biomarker-subdomain)

# Non-genetic Biomarkers subdomain

### **Variable label**: C-Reactive Protbein  
**Variable name**: bio_crp_0
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  complete
**Harmonization comment**: Study-specific variable is taken from fresh blood and participants were fasting with tea and toast.    
**R script**:  
```{r, echo=TRUE}
bio_LASA2_0$bio_crp_0 <- ifelse(LASA2B$bmcrp < 0,NA, as.numeric(LASA2B$bmcrp))
```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_1    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  impossible  
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```

### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_2    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:    

**Harmonization status**:  impossible  
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}
```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_3    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L   
**Category coding**:   

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_4    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:   

**Harmonization status**:  impossible  
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_5    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  impossible  
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_6    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:   

**Harmonization status**:  impossibe
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_0    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**:

**Harmonization status**: complete 
**Harmonization comment**: Study-specific variable is taken from fresh blood and participants were fasting with tea and toast.  
**R script**:  
```{r, echo=TRUE}
bio_LASA2_0$bio_tsh_0<- ifelse(LASA2B$bmtsh < 0, NA, as.numeric(LASA2B$bmtsh))
```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_1    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible
**Harmonization comment**: 

**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_2    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_3    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_4    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_5    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_6    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_0    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**:

**Harmonization status**:  complete  
**Harmonization comment**:  Study-specific variable is taken from fresh blood and participants were fasting with tea and toast.      
**R script**:  
```{r, echo=TRUE}
bio_LASA2_0$bio_t4_0<- ifelse(LASA2B$bmfreet4 < 0, NA, as.numeric(LASA2B$bmfreet4))
```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_1    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:   

**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_2    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_3    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_4    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_5    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_6    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_0    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  complete  
**Harmonization comment**: Study-specific variable is taken from fresh blood and participants were fasting with tea and toast.       
**R script**:  
```{r, echo=TRUE}
bio_LASA2_0$bio_alb_0<-ifelse(LASA2B$bmalbumi < 0, NA, as.numeric(LASA2B$bmalbumi))
```
### **Variable label**: Albumin  
**Variable name**: bio_alb_1    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_2    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  complete  
**Harmonization comment**: Study-specific variable is taken from fresh blood and participants were fasting.       
**R script**:  
```{r, echo=TRUE}
bio_LASA2_2$bio_alb_2<- ifelse(LASA2G$gmalbumi < 0, NA, as.numeric(LASA2G$gmalbumi))
```
### **Variable label**: Albumin  
**Variable name**: bio_alb_3    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_4    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**:   


**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_5    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_6    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_0    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   

**R script**:  
```{r, echo=TRUE}
```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_1    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_2    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_3    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_4    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_5    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 
```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_6    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
 
```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_0    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 
**Harmonization status**:  complete
**Harmonization comment**: Study-specific variable is taken from fresh blood and participants were fasting with tea and toast.       
**R script**:  
```{r, echo=TRUE}
bio_LASA2_0$bio_vitd_0<-LASA2B$bmvitd25st
#1 ng/ml =0.400641 nmol/l
bio_LASA2_0$bio_vitd_0[bio_LASA2_0$bio_vitd_0==-1]<-NA
bio_LASA2_0$bio_vitd_0<-bio_LASA2_0$bio_vitd_0*0.400641
```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_1    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**: impossible  
**Harmonization comment**:   

**R script**:  
```{r, echo=TRUE}
```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_2    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
bio_LASA2_2$bio_vitd_2 <- LASA2G$gmvitd25st
bio_LASA2_2[bio_LASA2_2$bio_vitd_2 == -1 | 
            bio_LASA2_2$bio_vitd_2 == -2,]$bio_vitd_2 <- NA
bio_LASA2_2$bio_vitd_2 <- bio_LASA2_2$bio_vitd_2*0.400641
```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_3    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_4    
**Variable description**: Vitamin D measured in serum (fresh and frozen).      
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_5    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_6    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 
**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_0    
**Variable description**: Triglycerides measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  complete  
**Harmonization comment**: Study-specific variable is taken from fresh blood and participants were fasting with tea and toast.        
**R script**:  
```{r, echo=TRUE}
bio_LASA2_0$bio_tg_0 <- ifelse(LASA2B$bmtrigly < 0,NA, as.numeric(LASA2B$bmtrigly))
```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_1    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  impossible   
**Harmonization comment**:  

**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_2    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_3    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_4    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_5    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_6    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```

# Genetic Biomarker subdomain

### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_0   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_1   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_2   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A 
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_3   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_4   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_5   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_6   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_0   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_1   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_2   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_3   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_4   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_5   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_6   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_0   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_1   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_2   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_3   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_4   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_5   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_6   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_0   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_1   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_2   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_3   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_4   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_5   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_6   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_0   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_1   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_2   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_3   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_4   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_5   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_6   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
