---
title: "Biomarkers and genetics DataSchema"
output: html_document
---

# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opalr)
library(data.table)
# Create an opal object with the login information
erasmus_opal <-opal.login()
#Login to Opal server and assign the content of the LASA table(s) to your RStudio environment

# LASA1B
opal.assign.table.tibble(erasmus_opal, 'LASA1B', 'LASA.LASA1B_biodata',variables = list('bmalbumi','bmtsh','bmcrp','bmtrigly','bmfreet4','bmhscrp'))
LASA1B <- opal.execute(erasmus_opal,'LASA1B')

# LASA1C
opal.assign.table.tibble(erasmus_opal, 'LASA1C', 'LASA.LASA1C_biodata',variables = list('cmalbumi','cmtsh','cmcrp','cmtrigly','cmfreet4','cmhscrp', "cmvitd25", "cmvitd25st","cmtsh2", "cmtrigl2", "cmft4", "cmft3"))
LASA1C <- opal.execute(erasmus_opal,'LASA1C')


# LASA1G
opal.assign.table.tibble(erasmus_opal, 'LASA1G', 'LASA.LASA1G_biodata',variables = list('gmalbumi',"gmvitd25", "gmvitd25st"))
LASA1G <- opal.execute(erasmus_opal,'LASA1G')

```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
bio_LASA1_0 <- data.frame(id = LASA1B$id)
bio_LASA1_1 <- data.frame(id = LASA1C$id)
bio_LASA1_6 <- data.frame(id = LASA1G$id)


```
## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
#opal.logout(erasmus_opal) 
```
# Table of Contents
1. [Non-genetic Biomarker subdomain](#Non-genetic-biomarker-subdomain)
2. [Genetic Biomarker subdomain](#Genetic-biomarker-subdomain)

# Non-genetic Biomarkers subdomain

### **Variable label**: C-Reactive Protbein  
**Variable name**: bio_crp_0    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  complete
**Harmonization comment**: Two variables used for harmonization. First variable is from frozen blood and participants were fasting with tea and toast. Second variable is from fresh blood and participants were non-fasting. Values from both variables are closely correlated. Values from frozen blood and fasting with tea and toast were taken first, and if there were missing values, values were taken from fresh blood and non-fasting.    
**R script**:  
```{r, echo=TRUE}
bio_LASA1_0$bio_crp_0 <- ifelse(
                          is.na(LASA1B$bmhscrp), 
                                LASA1B$bmcrp, 
                                LASA1B$bmhscrp)
bio_LASA1_0[bio_LASA1_0$bio_crp_0 == -1 | 
            bio_LASA1_0$bio_crp_0 == -2,]$bio_crp_0 <- NA
```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_1    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  complete
**Harmonization comment**:  Two variables used for harmonization. First variable is from frozen blood and participants were fasting. Second variable is from fresh blood and participants were fasting with tea and toast. Values from both variables are closely correlated. Values from frozen blood and fasting participants were taken first, and if there were missing values, values were taken from fresh blood and participants fasting with tea and toast.     
**R script**:  
```{r, echo=TRUE}
bio_LASA1_1$bio_crp_1 <- ifelse(
                          is.na(LASA1C$cmhscrp), 
                                LASA1C$cmcrp,
                                LASA1C$cmhscrp)
bio_LASA1_1[bio_LASA1_1$bio_crp_1 == -1 | 
            bio_LASA1_1$bio_crp_1 == -2,]$bio_crp_1<-NA
```

### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_2    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_3    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L   
**Category coding**:   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_4    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_5    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  impossible  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: bio_crp_6    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:   

**Harmonization status**:  impossibe
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_0    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**:

**Harmonization status**: complete     
**Harmonization comment**: Study-specific variable is taken from fresh blood and participants were non-fasting.    

**R script**:  
```{r, echo=TRUE}
bio_LASA1_0$bio_tsh_0 <- LASA1B$bmtsh
bio_LASA1_0[bio_LASA1_0$bio_tsh_0 == -1 |
            bio_LASA1_0$bio_tsh_0 == -2,]$bio_tsh_0 <- NA
```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_1    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  complete
**Harmonization comment**: Values from frozen and fresh are closely correlated so both variables were used for harmoniztation. Values from frozen were taken first, and if there were missing values, values were taken from fresh.    


**R script**:  
```{r, echo=TRUE}
bio_LASA1_1$bio_tsh_1 <- ifelse(
                          is.na(LASA1C$cmtsh2),
                                LASA1C$cmtsh,
                                LASA1C$cmtsh2)
bio_LASA1_1[bio_LASA1_1$bio_tsh_1 == -1 | 
            bio_LASA1_1$bio_tsh_1 == -2,]$bio_tsh_1 <- NA
```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_2    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_3    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_4    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_5    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: bio_tsh_6    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_0    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**:

**Harmonization status**:  complete      
**Harmonization comment**:    Study-specific values are from fresh blood and participants were non-fasting.  
```{r, echo=TRUE}
bio_LASA1_0$bio_t4_0 <- LASA1B$bmfreet4
bio_LASA1_0[bio_LASA1_0$bio_t4_0 == -1 |
            bio_LASA1_0$bio_t4_0 == -2,]$bio_t4_0 <- NA
```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_1    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**:

**Harmonization status**:  complete  
**Harmonization comment**: Values from frozen and fresh blood are closely correlated so both variables were used for harmoniztation. Values from frozen blood were taken first, and if there were missing values, values were taken from fresh blood.    

**R script**:  
```{r, echo=TRUE}
bio_LASA1_1$bio_t4_1 <- ifelse(
                         is.na(LASA1C$cmfreet4),
                               LASA1C$cmft4,
                               LASA1C$cmfreet4)
bio_LASA1_1[bio_LASA1_1$bio_t4_1 == -1 | 
            bio_LASA1_1$bio_t4_1==-2,]$bio_t4_1 <- NA
```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_2    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_3    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_4    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_5    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: bio_t4_6    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_0    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  complete  
**Harmonization comment**: Study-specific variable is taken from fresh blood and participants were non-fasting.       
**R script**:  
```{r, echo=TRUE}
bio_LASA1_0$bio_alb_0<-LASA1B$bmalbumi
bio_LASA1_0[bio_LASA1_0$bio_alb_0 == -1 | 
            bio_LASA1_0$bio_alb_0 == -2,]$bio_alb_0 <- NA
```
### **Variable label**: Albumin  
**Variable name**: bio_alb_1    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  complete 
**Harmonization comment**: Study-specific variable is taken from fresh blood and participants were fasting with tea and toast.       
**R script**:  
```{r, echo=TRUE}
bio_LASA1_1$bio_alb_1<-LASA1C$cmalbumi
bio_LASA1_1[bio_LASA1_1$bio_alb_1 == -1 | 
            bio_LASA1_1$bio_alb_1 == -2,]$bio_alb_1 <- NA
```
### **Variable label**: Albumin  
**Variable name**: bio_alb_2    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_3    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_4    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: N/A 


**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_5    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Albumin  
**Variable name**: bio_alb_6    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  complete    
**Harmonization comment**: Study-specific variable is taken from fresh blood and participants were fasting.  
**R script**:  
```{r, echo=TRUE}
bio_LASA1_6$bio_alb_6<-LASA1G$gmalbumi
bio_LASA1_6[bio_LASA1_6$bio_alb_6 == -1 | 
            bio_LASA1_6$bio_alb_6 == -2,]$bio_alb_6 <- NA
```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_0    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_1    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_2    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_3    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_4    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_5    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: bio_alt_6    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_0    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 
**Harmonization status**:  impossible
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_1    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**: complete   
**Harmonization comment**:  There are 2 variables of vitmain D available, the Odin standadised values were used for harmonization.  
**R script**:  
```{r, echo=TRUE}
# conversion: 0.400641
bio_LASA1_1$bio_vitd_1 <- LASA1C$cmvitd25st
bio_LASA1_1[bio_LASA1_1$bio_vitd_1 == -1 | 
            bio_LASA1_1$bio_vitd_1 == -2,]$bio_vitd_1 <- NA
bio_LASA1_1$bio_vitd_1 <- bio_LASA1_1$bio_vitd_1*0.400641
```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_2    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_3    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_4    
**Variable description**: Vitamin D measured in serum (fresh and frozen).      
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_5    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  complete    
**Harmonization comment**: There are 2 variables of vitmain D available, the Odin standadised values were used for harmonization.    
**R script**:  
```{r, echo=TRUE}
bio_LASA1_6$bio_vitd_6 <- LASA1G$gmvitd25st
bio_LASA1_6[bio_LASA1_6$bio_vitd_6 == -1 | 
            bio_LASA1_6$bio_vitd_6 == -2,]$bio_vitd_6 <-NA
bio_LASA1_6$bio_vitd_6 <- bio_LASA1_6$bio_vitd_6*0.400641
```
### **Variable label**: Vitamin D 
**Variable name**: bio_vitd_6    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 
**Harmonization status**:  impossible    
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_0    
**Variable description**: Triglycerides measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  complete  
**Harmonization comment**: Study-specific values are from fresh blood and participants were non-fasting.   
**R script**:  
```{r, echo=TRUE}
bio_LASA1_0$bio_tg_0<-LASA1B$bmtrigly
bio_LASA1_0[bio_LASA1_0$bio_tg_0 == -1 | 
            bio_LASA1_0$bio_tg_0 == -2,]$bio_tg_0 <- NA
```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_1    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  complete  
**Harmonization comment**: Two variables used for harmonization. First variable is from frozen blood and participants were fasting. Second variable is from fresh blood and participants were fasting with tea and toast. Values from both variables are closely correlated. Values from frozen blood and fasting were taken first, and if there were missing values, values were taken from fresh blood and fasting with tea and toast.      
**R script**:  
```{r, echo=TRUE}
bio_LASA1_1$bio_tg_1 <- ifelse(
                         is.na(LASA1C$cmtrigl2),
                               LASA1C$cmtrigly,
                               LASA1C$cmtrigl2)
bio_LASA1_1[bio_LASA1_1$bio_tg_1 == -1 |
            bio_LASA1_1$bio_tg_1 == -2,]$bio_tg_1 <- NA
```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_2    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  

**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_3    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_4    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_5    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Triglycerides 
**Variable name**: bio_tg_6    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```

# Genetic Biomarker subdomain

### **Variable label**: RS7412 
**Variable name**: bio_rs7412_0   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_1   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_2   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A 
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_3   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_4   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_5   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: bio_rs7412_6   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_0   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_1   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_2   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_3   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_4   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_5   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: bio_rs429358_6   
**Variable description**: RS429358 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_0   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_1   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_2   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_3   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_4   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_5   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: bio_rs440446_6   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_0   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_1   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_2   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_3   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_4   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: bio_rs6265_5   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Rs6265
**Variable name**: bio_rs6265_6   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_0   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_1   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_2   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_3   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_4   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_5   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: bio_rs11156739_6   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
