---
title: "Biomarkers and genetics DataSchema"
output: html_document
---

# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opalr)
library(data.table)
# Create an opal object with the login information
erasmus_opal <-opal.login()
#Login to Opal server and assign the content of the LASA table(s) to your RStudio environment

# LASA1B
opal.assign.table.tibble(erasmus_opal, 'LASA1B', 'LASA.LASA1B_biodata',variables = list('bmalbumi','bmtsh','bmcrp','bmtrigly','bmfreet4','bmhscrp'))
LASA1B <- opal.execute(erasmus_opal,'LASA1B')

# LASA1C
opal.assign.table.tibble(erasmus_opal, 'LASA1C', 'LASA.LASA1C_biodata',variables = list('cmalbumi','cmtsh','cmcrp','cmtrigly','cmfreet4','cmhscrp', "cmvitd25", "cmvitd25st","cmtsh2", "cmtrigl2", "cmft4", "cmft3"))
LASA1C <- opal.execute(erasmus_opal,'LASA1C')


# LASA1G
opal.assign.table.tibble(erasmus_opal, 'LASA1G', 'LASA.LASA1G_biodata',variables = list('gmalbumi',"gmvitd25", "gmvitd25st"))
LASA1G <- opal.execute(erasmus_opal,'LASA1G')

```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
bio_LASA1_0 <- data.frame(id = LASA1B$id)
bio_LASA1_1 <- data.frame(id = LASA1C$id)
bio_LASA1_6 <- data.frame(id = LASA1G$id)


```
## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
#opal.logout(erasmus_opal) 
```
###Replacing all -1's and -2's with NA's and checking the datasets

```{r, echo=FALSE}
bio_LASA1_0[bio_LASA1_0==-1|bio_LASA1_0==-2]<-NA
str(bio_LASA1_0)
View(bio_LASA1_0)

bio_LASA1_1[bio_LASA1_1==-1|bio_LASA1_1==-2]<-NA
str(bio_LASA1_1)

bio_LASA1_6[bio_LASA1_6==-1|bio_LASA1_6==-2]<-NA
str(bio_LASA1_6)

```
# Table of Contents
1. [Non-genetic Biomarker subdomain](#Non-genetic-biomarker-subdomain)
2. [Genetic Biomarker subdomain](#Genetic-biomarker-subdomain)

# Non-genetic Biomarkers subdomain

### **Variable label**: C-Reactive Protbein  
**Variable name**: BIO_CRP_0    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  complete
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, MESA, RS, HAPIEE (baseline only).  Correlation between frozen and fresh (bmhscrp and bmcrp) is 0.607 so both variables were used for harmoniztation. Values from bmhscrp were taken first, and if there were missing values, values were taken from bmcrp.  
**R script**:  
```{r, echo=TRUE}
bio_LASA1_0$bio_crp_0 <- ifelse(
                          is.na(LASA1B$bmhscrp), 
                                LASA1B$bmcrp, 
                                LASA1B$bmhscrp)
bio_LASA1_0[bio_LASA1_0$bio_crp_0 == -1 | 
            bio_LASA1_0$bio_crp_0 == -2,]$bio_crp_0 <- NA
```
### **Variable label**: C-Reactive Protein  
**Variable name**: BIO_CRP_1    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  complete
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}
bio_LASA1_1$bio_crp_1 <- ifelse(
                          is.na(LASA1C$cmhscrp), 
                                LASA1C$cmcrp,
                                LASA1C$cmhscrp)
bio_LASA1_1[bio_LASA1_1$bio_crp_1 == -1 | 
            bio_LASA1_1$bio_crp_1 == -2,]$bio_crp_1<-NA
```

### **Variable label**: C-Reactive Protein  
**Variable name**: BIO_CRP_2    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:    

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: BIO_CRP_3    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L   
**Category coding**:   

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: BIO_CRP_4    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:   

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: BIO_CRP_5    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:     

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: C-Reactive Protein  
**Variable name**: BIO_CRP_6    
**Variable description**: C-Reactive Protein measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mg/L  
**Category coding**:   

**Harmonization status**:  impossibe
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS 
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: BIO_TSH_0    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**:

**Harmonization status**: impossible   
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS

**R script**:  
```{r, echo=TRUE}

#**Question for cohort**: LASA documentation states the information on thyroid hormone is collected only at time point C, but we have it at time B. In time point C, the measurement they refer to for thyroid function is cmtsh2, not cmtsh. bmths, cmths measures are referred under "Routine measurements: Albumin and cholesterol". What is the difference?
  
  
# bio_LASA1_0$bio_tsh_0 <- LASA1B$bmtsh
# bio_LASA1_0[bio_LASA1_0$bio_tsh_0 == -1 | 
#             bio_LASA1_0$bio_tsh_0 == -2,]$bio_tsh_0 <- NA

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: BIO_TSH_1    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  complete
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS


**R script**:  
```{r, echo=TRUE}

#**Question for cohort**: There are two variables: cmtsh: Blood: TSH mU/L abd cmtsh2: thyroid-stimulating hormone (mU/l). There are a lot more missing values in cmtsh, and the documentation refers to cmtsh2 for TSH hormone; however we probably should ask about the difference. cmtsh is under Routine measurements: Albumin and cholesterol category. Which one should we refer to?

# propostion 1
bio_LASA1_1$bio_tsh_1 <- LASA1C$cmtsh2
bio_LASA1_1[bio_LASA1_1$bio_tsh_1==-1 | 
            bio_LASA1_1$bio_tsh_1==-2,]$bio_tsh_1 <- NA
# propostion 2
bio_LASA1_1$bio_tsh_1 <- ifelse(
                          is.na(LASA1C$cmtsh2),
                                LASA1C$cmtsh,
                                LASA1C$cmtsh2)
bio_LASA1_1[bio_LASA1_1$bio_tsh_1 == -1 | 
            bio_LASA1_1$bio_tsh_1 == -2,]$bio_tsh_1 <- NA
```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: BIO_TSH_2    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: BIO_TSH_3    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: BIO_TSH_4    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: BIO_TSH_5    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroid Stimulating Hormone  
**Variable name**: BIO_TSH_6    
**Variable description**:Thyroid Stimulating Hormone Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mU/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Thyroxine  
**Variable name**: BIO_T4_0    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**:

**Harmonization status**:  complete  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
table(LASA1B$bmfreet4 , useNA = "always")
bio_LASA1_0$bio_t4_0<-LASA1B$bmfreet4
table(bio_LASA1_0$bio_t4_0, useNA = "always")
summary(bio_LASA1_0$bio_t4_0)

```
### **Variable label**: Thyroxine  
**Variable name**: BIO_T4_1    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**:

**Harmonization status**:  complete  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**Harmonization comment**: There are 2 different variables for T4: cmft4 (free T4 (pmol/l)) and cmfreet4 (Blood: free T4 pMOL/L)

**R script**:  
```{r, echo=TRUE}
table(LASA1C$cmft4 , useNA = "always")
table(LASA1C$cmfreet4 , useNA = "always")

#T4 but less answers b  
t4_1<-LASA1C$cmft4
t4_1[LASA1C$cmft4==-2|LASA1C$cmft4==-1]<-NA
t4_2<-LASA1C$cmfreet4
t4_2[LASA1C$cmfreet4==-2|LASA1C$cmfreet4==-1]<-NA
#For each individual the results of the two T-4 variables correlate quite closely
lm(t4_1~t4_2)

bio_LASA1_1$bio_t4_1<-LASA1C$cmfreet4
table(bio_LASA1_1$bio_t4_1, useNA = "always")
summary(bio_LASA1_1$bio_t4_1)

```
### **Variable label**: Thyroxine  
**Variable name**: BIO_T4_2    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Thyroxine  
**Variable name**: BIO_T4_3    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Thyroxine  
**Variable name**: BIO_T4_4    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Thyroxine  
**Variable name**: BIO_T4_5    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Thyroxine  
**Variable name**: BIO_T4_6    
**Variable description**:Thyroxine Measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: pMol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 4 studies: CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Albumin  
**Variable name**: BIO_ALB_0    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  complete  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
table(LASA1B$bmalbumi , useNA = "always")
bio_LASA1_0$bio_alb_0<-LASA1B$bmalbumi
table(bio_LASA1_0$bio_alb_0, useNA = "always")
summary(bio_LASA1_0$bio_alb_0)

```
### **Variable label**: Albumin  
**Variable name**: BIO_ALB_1    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  complete 
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
table(LASA1C$cmalbumi , useNA = "always")
bio_LASA1_1$bio_alb_1<-LASA1C$cmalbumi
table(bio_LASA1_1$bio_alb_1, useNA = "always")
summary(bio_LASA1_1$bio_alb_1)

```
### **Variable label**: Albumin  
**Variable name**: BIO_ALB_2    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Albumin  
**Variable name**: BIO_ALB_3    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Albumin  
**Variable name**: BIO_ALB_4    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: N/A (continuous variable)  


**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Albumin  
**Variable name**: BIO_ALB_5    
**Variable description**: Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Albumin  
**Variable name**: BIO_ALB_6    
**Variable description**:Albumin measured in serum (fresh and frozen).  
**Value type**: Decimal 
**Variable unit**: G/L  
**Category coding**: 

**Harmonization status**:  complete
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
table(LASA1G$gmalbumi , useNA = "always")
bio_LASA1_6$bio_alb_6<-LASA1G$gmalbumi
table(bio_LASA1_6$bio_alb_6, useNA = "always")
summary(bio_LASA1_6$bio_alb_6)

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: BIO_ALT_0    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  
#there wasn't this variable in the LASA1B
```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: BIO_ALT_1    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: BIO_ALT_2    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: BIO_ALT_3    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: BIO_ALT_4    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: BIO_ALT_5    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Alanine Aminotransferase  
**Variable name**: BIO_ALT_6    
**Variable description**: Alanine Aminotransferase measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: U/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Vitamin D 
**Variable name**: BIO_VitD_0    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 
**Harmonization status**:  impossible
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Vitamin D 
**Variable name**: BIO_VitD_1    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**: complete   
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**Harmonization comment**:There are 2 variables: cmvitd25st (serum: 25-hydroxyvitamin D (25(OH)D), nmol/L, ODIN-standardized) and 
cmvitd25 (serum: 25-hydroxyvitamin D (25(OH)D), nmol/L). "In 2015, serum 25(OHD) values were standardized using the Vitamin D Standardization Program (VDSP) protocol as part of the European ODIN study" From NIH website (https://ods.od.nih.gov/Research/vdsp.aspx): "art of the ODS Vitamin D Initiative, VDSP is an international collaborative effort to standardize the laboratory measurement of vitamin D status." So should we use the standardized measure to make it more comparable across time and studies. However, if other cohorts didn't use this measure maybe there is not much point?
The unit of measurement is nmol/L in the study and ng/ml in the DS. So the units are converted to harmonize. 

**R script**:  
```{r, echo=TRUE}
table(LASA1C$cmvitd25st, useNA = "always")
table(LASA1C$cmvitd25, useNA = "always")

summary(LASA1C$cmvitd25)
summary(LASA1C$cmvitd25st)

bio_LASA1_1$bio_vitd_1<-LASA1C$cmvitd25st
#1 ng/ml =0.400641 nmol/l
table(bio_LASA1_1$bio_vitd_1, useNA = "always")
bio_LASA1_1$bio_vitd_1<-bio_LASA1_1$bio_vitd_1*0.400641
table(bio_LASA1_1$bio_vitd_1, useNA = "always")
summary(bio_LASA1_1$bio_vitd_1)

```
### **Variable label**: Vitamin D 
**Variable name**: BIO_VitD_2    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Vitamin D 
**Variable name**: BIO_VitD_3    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Vitamin D 
**Variable name**: BIO_VitD_4    
**Variable description**: Vitamin D measured in serum (fresh and frozen).      
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**:

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Vitamin D 
**Variable name**: BIO_VitD_5    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Vitamin D 
**Variable name**: BIO_VitD_6    
**Variable description**: Vitamin D measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: ng/ml  
**Category coding**: 
**Harmonization status**:  complete  
**Harmonization comment**: Available in 5 studies: CLSA, HUNT, LASA, MESA, RS  
**R script**:  
```{r, echo=TRUE}

table(LASA1G$gmvitd25st, useNA = "always")
table(LASA1G$gmvitd25, useNA = "always")

summary(LASA1G$gmvitd25st)
summary(LASA1G$gmvitd25)

bio_LASA1_6$bio_vitd_6<-LASA1G$gmvitd25st
bio_LASA1_6$bio_vitd_6<-bio_LASA1_6$bio_vitd_6*0.400641
table(bio_LASA1_6$bio_vitd_6, useNA = "always")
summary(bio_LASA1_6$bio_vitd_6)

```
### **Variable label**: Triglycerides 
**Variable name**: BIO_TG_0    
**Variable description**: Triglycerides measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  complete  
**Harmonization comment**: Available in 7 studies: CLSA, HUNT, LASA, RECORD, MESA, RS, HAPIEE (baseline only) 
**R script**:  
```{r, echo=TRUE}
table(LASA1B$bmtrigly, useNA = "always")
bio_LASA1_0$bio_tg_0<-LASA1B$bmtrigly
table(bio_LASA1_0$bio_tg_0, useNA = "always")
summary(bio_LASA1_0$bio_tg_0)

```
### **Variable label**: Triglycerides 
**Variable name**: BIO_TG_1    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  complete  
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**Harmonization comment**: There are 2 variables in the dataset.  cmtrigly (Blood: triglycerids mMOL/L), cmtrigl2 (Blood: triglycerids mmol/L). cmtrigl2 is specifically under Cholesterol, triglycerides and fructosamin, cmtrigly is under routine measures. For bmtrigly, for collection point B, the documentation mentions -2's are from the Oss region, maybe these routine measure were not taken from that region at time point C as well?

**R script**:  
```{r, echo=TRUE}
table(LASA1C$cmtrigly, useNA = "always")
table(LASA1C$cmtrigl2, useNA = "always")

tg1<-LASA1C$cmtrigly
tg1[LASA1C$cmtrigly==-2|LASA1C$cmtrigly==-1]<-NA
tg2<-LASA1C$cmtrigl2
tg2[LASA1C$cmtrigl2==-2|LASA1C$cmtrigl2==-1]<-NA

#For each individual the results of the two variables are close to each other
lm(tg1~tg2)

#cmtrigl2 has less missing cases
bio_LASA1_1$bio_tg_1<-LASA1C$cmtrigl2
table(bio_LASA1_1$bio_tg_1, useNA = "always")
summary(bio_LASA1_1$bio_tg_1)

```
### **Variable label**: Triglycerides 
**Variable name**: BIO_TG_2    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  

**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Triglycerides 
**Variable name**: BIO_TG_3    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Triglycerides 
**Variable name**: BIO_TG_4    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  impossible  
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Triglycerides 
**Variable name**: BIO_TG_5    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 
**Harmonization status**:  impossible  
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```
### **Variable label**: Triglycerides 
**Variable name**: BIO_TG_6    
**Variable description**: Triglycerides  Measured in serum (fresh and frozen).    
**Value type**: Decimal 
**Variable unit**: mmol/L  
**Category coding**: 

**Harmonization status**:  impossible  
**Harmonization comment**: Available in 6 studies: CLSA, HUNT, LASA, RECORD, MESA, RS 
**R script**:  
```{r, echo=TRUE}
#This is w### **Variable label**: Albumin  

```

# Genetic Biomarker subdomain

### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_0   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_1   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_2   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A 
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_3   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_4   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_5   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: RS7412 
**Variable name**: BIO_RS7412_6   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_0   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_1   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_2   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_3   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_4   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_5   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs429358 
**Variable name**: BIO_Rs429358_6   
**Variable description**: RS7412 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_0   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_1   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_2   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_3   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_4   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_5   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs440446 
**Variable name**: BIO_Rs440446_6   
**Variable description**: Rs440446 Polymorphism of APOE Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_0   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_1   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_2   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive 

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_3   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_4   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_5   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Rs6265
**Variable name**: BIO_Rs6265_6   
**Variable description**: Rs6265 Polymorphism of BDNF Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_0   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_1   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive  

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_2   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_3   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_4   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_5   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Rs11156739
**Variable name**: BIO_Rs11156739_6   
**Variable description**: Rs11156739 Polymorphism of PSEN2 Gene.    
**Value type**: alphanumeric  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Homozygous Dominant    
1 | Homozygous Recessive   
2 | Heterozygous Recessive

**Harmonization status**:  impossible  
**Harmonization comment**: GWAS available in CLSA, HUNT, LASA, RS
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
